Living on the edge: crop boundary effects on precision canola and wheat yields in Alberta

### 2021-09-17 Manuscript/manuscript.Rmd
Worked on filter functions

Yield data was collected in rectangles of the same length as the data interval (distance = combine ground speed $\times$ interval, typically 1 second) and the same width as the combine header (5-7 m, adjusted to account for overlap with adjacent swaths).
We extracted the size of each polygon (m$^2$), dry yield (tonnes), and the spatial location, and the sequence of collection (1 - end of harvest)
Because of the large number of yield rectangles per field (30-800 thousand), we used the centroid of each polygon as its location, treating areal data as point data
Seeding and application rates were constant across fields, so we did not consider inputs in our analysis
We used dry yield (tonnes of seed/hectare minus recorded crop moisture) as our measure of crop yield
Precision yield data can be highly variable and is prone to extreme outliers (both positive and negative), especially when combine ground speeds are low and at the beginning of rows [@]
Therefore, we filtered data that lay outside the 95th percentiles of yield within each field, values less than or equal to zero, and values outside of the 95th percentiles of ground speed.
Due to the large number of data at each field, we sub-sampled to 50,000 data points per field to reduce computation time.

>>>>

Yield data was collected in rectangles of the same length as the data interval (distance = combine ground speed $\times$ interval, typically 1 second) and the same width as the combine header (5-7 m, adjusted to account for overlap with adjacent swaths).
We extracted the size of each polygon (m$^2$), dry yield (tonnes), and the spatial location, and the sequence of collection (1 - end of harvest)
Because of the large number of yield rectangles per field (30-800 thousand), we used the centroid of each polygon as its location, treating areal data as point data
Seeding and application rates were constant across fields, so we did not consider inputs in our analysis
We used dry yield (tonnes of seed/hectare minus recorded crop moisture) as our measure of crop yield
Precision yield data can be highly variable and is prone to extreme outliers, especially when combine ground speeds are low and at the beginning of rows [@griffin2007; @whelan2013].
We filtered data that lay outside the 95th percentiles of yield within each field, values less than or equal to zero, and values outside of the 95th percentiles of ground speed.
Due to the large number of data at each field, we sub-sampled to 50,000 data points per field to reduce computation time.
